Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-06-24 paper.qmd
Add code to generate citations in tracked changes, close #46

```{r}
#| include: false
#| eval: false
remotes::install_dev("tmap")
library(tmap)
# Save title page (1st page of paper.pdf):
system("pdftk _site/paper.pdf cat 1 output _site/title_page.pdf")
# Combine cv.pdf with visions.pdf:
system("pdftk _site/cv.pdf _site/visions.pdf cat output _site/cv_and_visions.pdf")
# latexdiffr::latexdiff("paper-v1.qmd", "paper.qmd")
system("latexdiff paper-r1.tex paper.tex > tracked-changes-r2.tex")
system("pdflatex tracked-changes-r2.tex")
browseURL("tracked-changes-r2.pdf")
```

>>>>

```{r}
#| include: false
#| eval: false
remotes::install_dev("tmap")
library(tmap)
# # Save title page (1st page of paper.pdf):
# system("pdftk _site/paper.pdf cat 1 output _site/title_page.pdf")
# Combine cv.pdf with visions.pdf:
# system("pdftk _site/cv.pdf _site/visions.pdf cat output _site/cv_and_visions.pdf")
# latexdiffr::latexdiff("paper-v1.qmd", "paper.qmd")
system("latexdiff paper-r1.tex paper.tex > tracked-changes-r2.tex")
system("pdflatex tracked-changes-r2.tex")
# To debug this search for: 
# https://www.google.com/search?client=ubuntu-sn&channel=fs&q=latexdiff+references+question+marks
# From that: https://tex.stackexchange.com/questions/63852/question-mark-or-bold-citation-key-instead-of-citation-number
# Bibliography:
system("bibtex tracked-changes-r2.aux")
system("pdflatex tracked-changes-r2.tex")
system("pdflatex tracked-changes-r2.tex")

browseURL("tracked-changes-r2.pdf")
```
